Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-02 gibbs.tex
Update gibbs.tex

\paragraph{Algorithm}
The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
The simulation algorithm is following:
\begin{enumerate}
\item Simulate molecular dynamics in both boxes; collect the observables, for example, values of pressure $P$, to an array; 
\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, 
%$\nna\gel$,
$\Ncl\gel$ 
%$\nna\out$ 
and $\Ncl\out$ ; 
\item Repeat the procedure until the desired length of sample arrays is reached.
\end{enumerate}

>>>>

\paragraph{Algorithm}
The thermodynamic equilibrium between the two subvolumes implies the exchange of ion pairs between them.
This is performed by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.

As mentioned above, the simulation consists of MD and MC subsimulations. The algorithm is following:
\begin{enumerate}
\item Simulate MD in both boxes and collect the observables (pressure, $P$)
\item Perform MC procedure simulating ion exchange and collect the observables (number of ions in both boxes, 
%$\nna\gel$,
$\Ncl\gel$ 
%$\nna\out$ 
and $\Ncl\out$ )
\item Repeat the procedure until the desired length of sample arrays is reached.
\end{enumerate}
